taxize - taxonomic search and retrieval in R

### 2013-06-10 inst/doc/taxize_withcode_appA.tex
revert additions in edisz-dev_ms_branch

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage[titletoc, title]{appendix}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\begin{appendices}
\section{A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# The tnrs function accepts a vector of 1 or more}
splist_tnrs <- \hlfunctioncall{tnrs}(query = splist, getpost = \hlstring{"POST"}, source_ = \hlstring{"iPlant_TNRS"})

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
           submittedName         acceptedName    sourceId score
3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
10       Rosa california     Rosa californica iPlant_TNRS  0.99
9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS  1.00
6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# So here's our updated species list}
(splist <- \hlfunctioncall{as.character}(splist_tnrs$acceptedName))
\end{alltt}
\begin{verbatim}
 [1] "Helianthus annuus"    "Pinus contorta"       "Collomia grandiflora"
 [4] "Abies magnifica"      "Rosa californica"     "Datura wrightii"     
 [7] "Mimulus bicolor"      "Nicotiana glauca"     "Madia sativa"        
[10] "Bartlettia scaposa"  
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
tsns <- \hlfunctioncall{get_tsn}(searchterm = splist, searchtype = \hlstring{"sciname"}, verbose = FALSE)
comnames <- \hlfunctioncall{lapply}(tsns, getcommonnamesfromtsn)

\hlcomment{# Unfortunately, common names are not standardized like species names, so}
\hlcomment{# there are multiple common names for each taxon}
\hlfunctioncall{sapply}(comnames, length)
\end{alltt}
\begin{verbatim}
 [1] 3 3 3 3 3 3 3 3 3 3
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# And we can make a data.frame of our scientific and common names}
(allnames <- \hlfunctioncall{data.frame}(spname = splist, comname = comnames_vec))
\end{alltt}
\begin{verbatim}
                 spname                       comname
1     Helianthus annuus              common sunflower
2        Pinus contorta                lodgepole pine
3  Collomia grandiflora        largeflowered collomia
4       Abies magnifica                    golden fir
5      Rosa californica           California wildrose
6       Datura wrightii            sacred thorn-apple
7       Mimulus bicolor yellow and white monkeyflower
8      Nicotiana glauca                  tree tobacco
9          Madia sativa                 coast tarweed
10   Bartlettia scaposa                Bartlett daisy
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# As we already have Taxonomic Serial Numbers from ITIS, let's just get}
\hlcomment{# classifications from ITIS. Note that we could use NCBI instead.}
class_list <- \hlfunctioncall{classification}(tsns)
\hlfunctioncall{sapply}(class_list, nrow)
\end{alltt}
\begin{verbatim}
 [1] 12 11 12 11 12 12 12 12 12 12
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# Now that we have allnames_df, we can start to see some relationships}
\hlcomment{# among species simply by their shared taxonomic names}
allnames_df[1:2, ]
\end{alltt}
\begin{verbatim}
              spname        comname Kingdom     Subkingdom Infrakingdom
1    Abies magnifica     golden fir Plantae Viridaeplantae Streptophyta
2 Bartlettia scaposa Bartlett daisy Plantae Viridaeplantae Streptophyta
      Division     Subdivision Infradivision         Class Superorder
1 Tracheophyta Spermatophytina  Gymnospermae     Pinopsida       <NA>
2 Tracheophyta Spermatophytina  Angiospermae Magnoliopsida  Asteranae
      Order     Family      Genus
1   Pinales   Pinaceae      Abies
2 Asterales Asteraceae Bartlettia
\end{verbatim}
\begin{alltt}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=4in,height=4in]{figure/phylogeny}

}

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(rgbif)
\hlfunctioncall{library}(ggplot2)

\hlcomment{# get occurences}
occurr_list <- \hlfunctioncall{occurrencelist_many}(\hlfunctioncall{as.character}(allnames$spname), coordinatestatus = TRUE, 
    maxresults = 100, removeZeros = TRUE, fixnames = \hlstring{"changealltorig"})

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 3, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}()) + 
    \hlfunctioncall{coord_equal}()
p
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\textwidth]{figure/map}

}

@@

\caption{a map...} 
\end{figure}

\end{appendices}
\end{document}

>>>>

\section{A complete reproducible workflow, from a species list to a phylogeny, and distribution map.}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# The tnrs function accepts a vector of 1 or more}
splist_tnrs <- \hlfunctioncall{tnrs}(query = splist, getpost = \hlstring{"POST"}, source_ = \hlstring{"iPlant_TNRS"})
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Calling http://taxosaurus.org/retrieve/679c69546d1311b72ce97f5ad1101254}}\begin{alltt}

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
##            submittedName         acceptedName    sourceId score
## 3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
## 1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
## 4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
## 5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
## 10       Rosa california     Rosa californica iPlant_TNRS  0.99
## 9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
## 7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
## 8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS  1.00
## 6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
## 2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# So here's our updated species list}
(splist <- \hlfunctioncall{as.character}(splist_tnrs$acceptedName))
\end{alltt}
\begin{verbatim}
##  [1] "Helianthus annuus"    "Pinus contorta"       "Collomia grandiflora"
##  [4] "Abies magnifica"      "Rosa californica"     "Datura wrightii"     
##  [7] "Mimulus bicolor"      "Nicotiana glauca"     "Madia sativa"        
## [10] "Bartlettia scaposa"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
tsns <- \hlfunctioncall{get_tsn}(searchterm = splist, searchtype = \hlstring{"sciname"}, verbose = FALSE)
comnames <- \hlfunctioncall{lapply}(tsns, getcommonnamesfromtsn)
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=36616}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=183327}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=31037}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=181834}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=24818}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=30521}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=33245}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=30574}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=38040}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getCommonNamesFromTSN?tsn=36822}}\begin{alltt}

\hlcomment{# Unfortunately, common names are not standardized like species names, so}
\hlcomment{# there are multiple common names for each taxon}
\hlfunctioncall{sapply}(comnames, length)
\end{alltt}
\begin{verbatim}
##  [1] 3 3 3 3 3 3 3 3 3 3
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# And we can make a data.frame of our scientific and common names}
(allnames <- \hlfunctioncall{data.frame}(spname = splist, comname = comnames_vec))
\end{alltt}
\begin{verbatim}
##                  spname                       comname
## 1     Helianthus annuus              common sunflower
## 2        Pinus contorta                lodgepole pine
## 3  Collomia grandiflora        largeflowered collomia
## 4       Abies magnifica                    golden fir
## 5      Rosa californica           California wildrose
## 6       Datura wrightii            sacred thorn-apple
## 7       Mimulus bicolor yellow and white monkeyflower
## 8      Nicotiana glauca                  tree tobacco
## 9          Madia sativa                 coast tarweed
## 10   Bartlettia scaposa                Bartlett daisy
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# As we already have Taxonomic Serial Numbers from ITIS, let's just get}
\hlcomment{# classifications from ITIS. Note that we could use uBio instead.}
class_list <- \hlfunctioncall{classification}(tsns)
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=36616}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=183327}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=31037}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=181834}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=24818}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=30521}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=33245}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=30574}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=38040}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# http://www.itis.gov/ITISWebService/services/ITISService/getFullHierarchyFromTSN?tsn=36822}}\begin{alltt}
\hlfunctioncall{sapply}(class_list, nrow)
\end{alltt}
\begin{verbatim}
##  [1] 12 11 12 11 12 12 12 12 12 12
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# Now that we have allnames_df, we can start to see some relationships}
\hlcomment{# among species simply by their shared taxonomic names}
allnames_df[1:2, ]
\end{alltt}
\begin{verbatim}
##               spname        comname Kingdom     Subkingdom Infrakingdom
## 1    Abies magnifica     golden fir Plantae Viridaeplantae Streptophyta
## 2 Bartlettia scaposa Bartlett daisy Plantae Viridaeplantae Streptophyta
##       Division     Subdivision Infradivision         Class Superorder
## 1 Tracheophyta Spermatophytina  Gymnospermae     Pinopsida       <NA>
## 2 Tracheophyta Spermatophytina  Angiospermae Magnoliopsida  Asteranae
##       Order     Family      Genus
## 1   Pinales   Pinaceae      Abies
## 2 Asterales Asteraceae Bartlettia
\end{verbatim}
\begin{alltt}

@@

\begin{figure}[!h] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# Fetch phylogeny from phylomatic}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: No parallel backend registered}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: executing \%dopar\% sequentially: no parallel backend registered}}\begin{alltt}
\hlcomment{# Format teeth-labels}
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlcomment{# plot phylogeny}
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}
\includegraphics[width=4in,height=4in]{figure/phylogeny}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(rgbif)
\hlfunctioncall{library}(ggplot2)

\hlcomment{# get occurences}
occurr_list <- \hlfunctioncall{occurrencelist_many}(\hlfunctioncall{as.character}(allnames$spname), coordinatestatus = TRUE, 
    maxresults = 100, removeZeros = TRUE, fixnames = \hlstring{"changealltorig"})
\end{alltt}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: NAs introduced by coercion}}\begin{alltt}

\hlcomment{# Make a map}
p <- \hlfunctioncall{gbifmap}(occurr_list) + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(title = \hlstring{""}, nrow = 3, 
    byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"}, legend.key = \hlfunctioncall{element_blank}()) + 
    \hlfunctioncall{coord_equal}()
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Rendering map...plotting 623 points}}\begin{alltt}
p
\end{alltt}
\end{kframe}\begin{figure}[h]

\includegraphics[width=.9\textwidth]{figure/plot_map} \caption[A map]{A map\label{fig:mapplot_map}}
\end{figure}

@@
